---
title: "Weight Tracker"
author: "Kevin Ren"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(car)
library("ggplot2")
library(tidyverse)
library(lubridate)
library(forecast)
weight <- read.csv("Downloads/weightjuly3.csv", header=TRUE, stringsAsFactors = FALSE)
morning <- weight$waking.up
night <- weight$at.night
date <- as.Date(weight$date, "%m/%d")
weight$index <- c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18)
index <- weight$index
```

# Plotting Morning Weight

```{r}
plot(morning~date, type="b", ylab="Morning Weight",xlab="Date")
title("The State of the Cut")
```

# Plotting Nighttime Weight

```{r}
plot(night~date, type="b", ylab="Nighttime Weight",xlab="Date")
title("The State of the Cut")
```


# Linear Regression of Morning and Nighttime Weights With Respect to Time

```{r}
morning_lm <- lm(morning~index)
summary(morning_lm)

night_lm <- lm(night~index)
summary(night_lm)
```

# Incorporating Both Plots and Regressions

```{r}
cool_double_plot <- ggplot(weight, aes(date, group="1")) +
  geom_line(aes(y=waking.up, color="Waking Up")) +
  geom_line(aes(y=at.night,color="Before Bed")) +
  ggtitle("State of the Cut") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Date") + 
  ylab("Weight") + 
  geom_abline(slope = coef(night_lm)[["index"]], 
              intercept = coef(night_lm)[["(Intercept)"]], color="dodgerblue1") +
  geom_abline(slope = coef(morning_lm)[["index"]], 
              intercept = coef(morning_lm)[["(Intercept)"]], color="lightsalmon2") +
  scale_colour_manual(values = c("dodgerblue1", "lightsalmon2")) 
cool_double_plot
```

# Forecasting

## Linear Modeling

Weight by August (according to linear regression):
```{r}
august_p <- as.data.frame(47)
colnames(august_p) = "index"
```

Morning:
```{r}
predict(morning_lm, newdata=august_p)
```

"Nighttime:"
```{r}
predict(night_lm, newdata=august_p)
```

## Time Series Analysis

```{r}
weight.ts <- ts(cbind(morning, night),
start = decimal_date(ymd("2022-06-15")),
                    frequency = 365)
plot(weight.ts, xlab ="Day",
    main ="TS of Weight",
    col.main ="darkgreen")
```

### Plotting TS Predictions using Arima Model

```{r}
morning_weight.ts <- ts(morning,
start = decimal_date(ymd("2022-06-15")),
                    frequency = 1)
night_weight.ts <- ts(night,
start = decimal_date(ymd("2022-06-15")),
                    frequency = 1)
morning.fit <- auto.arima(morning_weight.ts)
night.fit <- auto.arima(night_weight.ts)
```
 
### Next 47 forecasted values (up to August 1)
Morning:
```{r}
forecast(morning.fit, 47)
```
Night:
```{r}
forecast(night.fit, 47)
```


### Plotting the graph with forecasted values
```{r}
plot(forecast(morning.fit, 45), xlab ="Day",
ylab ="Weight",
main ="How Will the Cut Progress? Morning Edition", col.main ="darkgreen")

plot(forecast(night.fit, 45), xlab ="Day",
ylab ="Weight",
main ="How Will the Cut Progress? Night Edition", col.main ="darkgreen")
```



